%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plasmati Graduate CV
% LaTeX Template
% Version 1.0 (24/3/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati (alessandro.plasmati@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template needs to be compiled with XeLaTeX.
% The main document font is called Fontin and can be downloaded for free
% from here: http://www.exljbris.com/fontin.html
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%========================================================================================
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%========================================================================================

\documentclass[a4paper,10pt]{article} % Default font size and paper size

\usepackage{fontspec} % For loading fonts
\defaultfontfeatures{Mapping=tex-text}
\setmainfont[
  SmallCapsFont={Fontin Sans}
]{Ubuntu} % Main document font

\usepackage{fontspec,url,parskip} % Formatting packages

\usepackage[usenames,dvipsnames]{xcolor} % Required for specifying custom colors

% To reduce the height of the top margin uncomment:
\usepackage[top=1.5cm,bottom=1.5cm,left=2.5cm,right=2.5cm]{geometry}

\usepackage{hyperref} % Required for adding links	and customizing them
\definecolor{linkcolour}{rgb}{0,0.2,0.6} % Link color
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour} % Set link colors throughout the document

\usepackage{titlesec} % Used to customize the \section command
\newcommand*{\justifyheading}{\raggedright}
\titleformat{\section}{\Large\scshape\justifyheading}{}{0em}{}[\titlerule] % Text formatting of sections
\titlespacing{\section}{0pt}{3pt}{3pt} % Spacing around sections

\usepackage{tabularx}
\usepackage{array}
\usepackage{enumitem}

\usepackage[british]{babel}

\begin{document}

\pagestyle{empty} % Removes page numbering
\setlist{after=\vspace{-1\baselineskip}}
% No hyphens plz
\hyphenpenalty=10000
\exhyphenpenalty=10000

%========================================================================================
%	NAME AND CONTACT INFORMATION
%========================================================================================

\centering{\huge \textsc{Daniel Strong}\bigskip}\\ % Your name
\hrule
\footnotesize
{\begin{tabularx}{\textwidth}{lXr}
\href{mailto:dstrong@glyx.co.uk}{dstrong@glyx.co.uk} & & {Flat 4, Smith's Yard, Blossom Street}\\
{0758 315 81 81}                                     & & {Manchester}\\
                                                     & & {M46AJ}
\end{tabularx}}

%========================================================================================
%	Summary
%========================================================================================
\begin{flushleft}
Perpetually curious DevOps engineer with a passion for exploring new technologies.
\end{flushleft}

%========================================================================================
%	WORK EXPERIENCE
%========================================================================================

\section{\textsc{Work Experience}}
\centering
\begin{tabularx}{\textwidth}{r|X}

\textbf{Nov 2017 -- Present}        & \textbf{Platform Engineer} at The Co-operative Group \\
                                    & \emph{Manchester, UK} \\
                                    & \\
                                    & \footnotesize
    {Since starting in November 2017 I have worked on several teams across
    Co-op's Digital division, the department driving the Co-op's Digital
    Transformation program, building modern web services on AWS and Azure.
    \begin{itemize}
    \item I built out an implementation of Kong API gateway, starting from a
        prototype left by a departing engineer. I used open source tools to
        build an automated deployment pipeline for version controlled YAML
        config, and wrote and maintained comprehensive operational
        documentation.
    \item On the Membership team, I was responsible for supporting the complex
        array of Java services that underpins the Membership website. This old
        part of the Co-op Digital estate is tightly integrated with legacy
        Co-op IT systems; by necessity this position involved a lot of reactive
        work and prioritisation of incidents.  Nevertheless, with the support
        of the team, I managed to make significant improvements to the
        infrastructure while I was there, such as reducing deployment times by
        a factor of 10 by rolling out prebuilt AMIs provisioned with Packer. I
        also worked on the Digital Offers project, helping build out a
        serverless solution for managing digital coupons powered by AWS Lambda
        and AWS API Gateway.
    \item For the Health team, I built out the API infrastructure for the Co-op
        Health App, a mobile app which allows users to manage and order repeat
        prescriptions.  Working in a tight-knit multidisciplinary team, I
        rolled out a major refactor of the Terraform template used elsewhere in
        Co-op Digital.  Leveraging my experiences with Kong, I provided
        architectural guidance to developers on API implementation and
        management, designing and documenting the OAuth2.0 authentication flow
        used by the mobile app and the building a configuration management
        pipeline for AWS API Gateway based on version controlled OpenAPI
        specifications.
    \end{itemize}}\\

\multicolumn{2}{r}{} \\ %----------------------------------------------------------------

\textbf{Nov 2016 -- Oct 2017}        & \textbf{WebOps Engineer} at HM Revenue \& Customs \\
                                    & \emph{London, UK} \\
                                    & \\
                                    & \footnotesize
    {As part of HMRC Digital's WebOps Engineering team, I built, maintained and
    extended the Multi-channel Digital Tax Platform (MDTP), a docker-based PaaS
    which hosts HMRC's digital services.
    \begin{itemize}
    \item Lead the reimplementation of MDTP on AWS and reduced the size of the
    infrastructure codebase (in lines of code) by an order of magnitude,
    massively reducing architectural complexity and simplifying platform
    maintenance.
    \item Trained and upskilled new joiners, allowing the migration to continue
    despite a staggering loss of 75\% of our engineering team due to tax code
    changes.
    \item Collaborated with development teams to ensure a smooth, zero-downtime
    switch-over to AWS, minimising disruption both to services' release cycles
    and to our customers.
    \end{itemize}}\\

\multicolumn{2}{r}{} \\ %----------------------------------------------------------------

\textbf{Nov 2015 -- Nov 2016}       & \textbf{DevOps Support Engineer} at HM Revenue \& Customs \\
                                    & \emph{London, UK} \\
                                    & \footnotesize
    {\begin{itemize}[after=\vspace{-2\baselineskip}]
    \item Streamlined incident response and resolution by establishing a triage
    rota and work-in-progress limits, resulting in the elimination of a backlog
    which had fluctuated between 20 and 60 tickets since I joined.
    \item Coordinated proactive monitoring of release-critical pre-production
    environments, leading to a marked reduction in disruption to service
    development teams.
    \item Implemented predictive monitoring for simple trends like disk usage
    using linear regression.
    \end{itemize}}\\

\multicolumn{2}{r}{} \\ %----------------------------------------------------------------

\textbf{Jul 2014 -- Jul 2015}     & \textbf{Junior Developer} at {Nektarina Non-Profit}\\
                                    & \emph{Lancaster, UK}\\
                                    & \footnotesize
    {\begin{itemize}
    \item Built a questionnaire web application with Django, Python and postgreSQL
    \item Maintained several Wordpress installations on a LAMP (Linux, Apache,
    MySQL, PhP) on CentOS stack.
    \end{itemize}}\\

\end{tabularx}

%========================================================================================
%	COMPUTER SKILLS
%========================================================================================

\section{\textsc{Skills}}
\begin{tabularx}{\textwidth}{p{0.3cm}|p{4cm}X}
%----------------------------------------------------------------------------------------
\multicolumn{2}{l}{\textbf{DevOps}} & \\
\multicolumn{3}{c}{} \\ % - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
   & Linux:                              & Debian, RHEL, Arch Linux; and derivatives (Ubuntu, CentOS,
                                           \emph{etc.}) \\
     \\
   & Configuration management:           & Terraform, Packer, Ansible, Puppet \\
     \\
   & Public Cloud:                       & Load balancing and autoscaling, IAM; AWS S3, Lambda, API Gateway; some exposure to Azure, AKS\\
     \\
   & Logging and monitoring:             & Elasticsearch, Logstash, Kibana (ELK stack); Sensu, Graphite,
                                           collectd \\
     \\
   & Databases:                          & MongoDB, postgreSQL, MySQL/MariaDB \\
     \\
   & Virtualisation, containerisation:   & Docker (and a little kubernetes), Vagrant, Virtualbox \\
     \\
   & Continuous Integration:             & Jenkins, GitLabCI, Travis, CircleCI \\
\multicolumn{3}{c}{} \\ %----------------------------------------------------------------
\multicolumn{2}{l}{\textbf{Programming Languages}}      & \\
\multicolumn{3}{c}{} \\ % - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
  &  Advanced:                           & Python, Bash \\
     \\
  &  Basic                               & Go, Rust, Ruby, Javascript\\
\end{tabularx}

%========================================================================================
%	LANGUAGES
%========================================================================================
\bigskip
\begin{minipage}[t]{0.75\textwidth}
\section{Online}
\begin{tabular}{l}
\href{https://github.com/ouroboros8}{github.com/ouroboros8}\\
\href{https://www.linkedin.com/in/dstrong52}{linkedin.com/in/dstrong52}
\end{tabular}
\end{minipage}\hspace{-0.01\textwidth}
%
%========================================================================================
%	INTERESTS AND ACTIVITIES
%========================================================================================
%
\begin{minipage}[t]{0.25\textwidth}
\renewcommand{\justifyheading}{\raggedleft}
\section{\textsc{Languages}}
\begin{tabular}{rl}
 \textbf{English:} & Mother tongue  \\

 \textbf{Spanish:} & Native level  \\

 \textbf{Italian:} & Fluent  \\

 \textbf{Catalan:} & Fluent  \\

 \textbf{French:}  & Conversational
\end{tabular}
\end{minipage}

\end{document}
